Project Protocol

### 2019-10-18 protocol.Rmd
tweaked data privacy

During the project, datasets produced from the project and that are approved for public access will be made available via QUT's Research Data Finder. These will be deidentified and require only the necessary answers for the research to be reproducible.

##	Confidentially and privacy
Datasets produced from the project and that will not be available for public access will contain demographic information about the participants. If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.

@@

Responses to the survey will be stored securely using a private google drive accessible only to the researchers during the study through their password protected google drive accounts. This will contain potentially identifiable information if the respondents provide personal demographic information.

@@

This data set will also be deidentified and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations. 
The records of data analysis undertaken and the deidentified data will be stored on github as well as on QUT network drives.

@@

The analysis scripts and the data collected will be available for secondary use by other researchers to reproduce these results and also be used in future studies. This will be communicated to participants in their consent form.

>>>>

Research expectations today require that publications use reproducible research protocols, requiring data to be available. De-identified, and privatised data will be made available will be made available via QUT's Research Data Finder, and, if required by the publisher, once the results are published also available on the journal article web site.

##	Confidentially and privacy

Datasets produced from the project and that will *not* be available for public access will contain original demographic information about the participants and only the anonymous Figure-Eight contributor ID.

Datasets produced from the project and that *will be* available for public access on github will be de-identified and only contain the responses to survey.
If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.

@@

Responses to the survey will be stored securely using a private google drive accessible only to the researchers during the study through their password protected google drive accounts. This will contain the demographic information, at the coarse resolution specified in the data collection.

@@

This data set will also be de-identified, by removing the demographic data, and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations. The records of data analysis undertaken and the de-identified data will be stored on github as well as on QUT network drives.

@@

The analysis scripts and the de-identified data will be available for secondary use by other researchers to reproduce these results and also use in future studies. Participants will be asked to provide consent for this usage in the consent form.
